\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel} % Cambiado a inglés
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{hyperref}

% -------------------- Layout --------------------
\geometry{left=0.75in, right=0.75in, top=0.75in, bottom=0.75in}

\titlespacing*{\section}{0pt}{2pt plus 1pt minus 1pt}{8pt plus 1pt minus 1pt}
\titleformat{\section}
  {\normalfont\Large\bfseries}{}{0pt}{}[\vspace{-3pt}\titlerule\vspace{-4pt}]

\setlist[itemize]{left=0pt, topsep=2pt, partopsep=0pt, parsep=0pt, itemsep=1pt, after=\vspace{-2pt}}
\setlength{\parskip}{3pt plus 1pt minus 1pt}

\begin{document}
\pagestyle{empty}

\begin{center}
    {\LARGE \textbf{Benjamin Schindler}} \\
    \vspace{0.15cm}
    \textbf{CTO | AI Engineer} \\
    \vspace{0.05cm}
    \textbf{Master of Science in Data Science} \\
    \vspace{0.15cm}
    +(56 9) 56279434 \hspace{0.5cm} \texttt{benjamin.schindlerv@gmail.com} \\
    \vspace{0.05cm}
    % REMINDER: Change this when you customize your LinkedIn URL
    \href{https://www.linkedin.com/in/benjamin-schindler-92881a2b2/}{LinkedIn}
\end{center}

\section*{Profile}
Product-oriented AI Engineer focused on agentic systems, RAG, and production deployment. I build end-to-end solutions: from architectural design and integration with clinical/business stakeholders to rollout with observability and metrics, continuously iterating to maximize impact on end users.

\section*{Experience}
\begin{itemize}[left=0pt,noitemsep,nolistsep]

    \item \textbf{Doctor911} \hfill \textit{Mar. 2025 -- Present} \\
    \textit{Chief Technology Officer (CTO)} \hfill \textit{Jan. 2026 -- Present} \\
    - Leading technical strategy, roadmap, and execution, prioritizing architectural design and team coordination. \\
    - Defining engineering standards (quality, security, observability) and optimizing the delivery process (CI/CD). \\
    - Designing and developing AI/Data Science products (Agents, RAG), ensuring reliability and scalability. \\
    - Integrating end-to-end clinical and business workflows (WhatsApp/web), ensuring traceability and clear metrics. \\
    - Focus on impact: reduced purchase friction and improved recommendation experience for end users. \\

    \textit{AI Engineer} \hfill \textit{Mar. 2025 -- Jan. 2026} \\
    - Built multi-agent chatbots (LangGraph) with RAG and context management integrated into WhatsApp Business and web. \\
    - Implemented native payments and catalogs in WhatsApp for automated exam recommendations and purchasing. \\
    - Developed data pipelines and production services, evaluating and applying iterative improvements with real feedback. \\
    - Deployed cloud infrastructure (Cloud Run, Vertex AI) with advanced monitoring to ensure high availability. \\

    \item \textbf{WiseConn Latam} \hfill \textit{Dec. 2024 -- Mar. 2025} \\
    \textit{Data Science Intern} \\
    - Performed time series forecasting with deep models (Transformers/CNN/LSTM): cleaning and training. \\
    - Implemented reproducible pipelines and experimentation to compare approaches (metrics, validation, tracking). \\
    - Integrated models into AWS (SageMaker, S3), enabling efficient consumption and pipeline traceability. \\

    \item \textbf{Unitti} \hfill \textit{Sep. 2023 -- Jul. 2024} \\
    \textit{Intern (Software Engineer $\rightarrow$ AI)} \\
    - Developed Python APIs on PostgreSQL with automated testing, improving backend stability and response times. \\
    - Created a "Natural Language $\rightarrow$ SQL" App (Flask, LLMs, Azure/GCP) for business queries in natural language. \\
    - Iterated the product with real users to improve query accuracy and response clarity. \\

\end{itemize}

\section*{Education}
\begin{itemize}[left=0pt,itemsep=0.3em]
    \item \textbf{Universidad Adolfo Ibáñez} --- \textit{Master of Science in Data Science} \hfill \textit{2024 -- Present}
    \item \textbf{Universidad Adolfo Ibáñez} --- \textit{Computer Engineering} \hfill \textit{2020 -- Jul. 2025}
    \item \textbf{Universidad Adolfo Ibáñez} --- \textit{Industrial Engineering} \hfill \textit{2020 -- Jul. 2025}
\end{itemize}

\section*{Additional Information}
\begin{itemize}[left=0pt,noitemsep,nolistsep]
    \item \textbf{Skills:} Python, Pandas, SQL/NoSQL, TensorFlow; LLMs: LangChain/LangGraph, RAG; Cloud: GCP (Vertex AI, Cloud Run), AWS; Web: TypeScript, React; DevOps: Linux, CI/CD, Monitoring.
    \item \textbf{Languages:} English (Advanced), German (Basic).
\end{itemize}

\end{document}