\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}

% -------------------- Layout --------------------
\geometry{left=0.5in, right=0.5in, top=0.35in, bottom=0.35in}

\titlespacing*{\section}{0pt}{4pt plus 1pt minus 1pt}{3pt plus 1pt minus 0pt}
\titleformat{\section}
  {\normalfont\large\bfseries}{}{0pt}{}[\vspace{-3pt}\titlerule\vspace{-1pt}]

\setlist[itemize]{left=0pt, topsep=1pt, partopsep=0pt, parsep=0pt, itemsep=0pt, after=\vspace{-2pt}}
\setlength{\parskip}{1pt plus 1pt minus 1pt}

\begin{document}
\pagestyle{empty}

\begin{center}
    {\LARGE \textbf{Benjamin Schindler}} \\
    \vspace{0.06cm}
    \textbf{AI Engineer \& AI Engineering Lead} \\
    \vspace{0.02cm}
    \textbf{Agentic AI Systems | RAG | Product AI | M.Sc. Data Science} \\
    \vspace{0.06cm}
    +(56 9) 56279434 \hspace{0.35cm} \texttt{benjamin.schindlerv@gmail.com} \hspace{0.35cm} Santiago, Chile \\
    \vspace{0.02cm}
    \href{https://www.linkedin.com/in/benjamin-schindler-92881a2b2/}{LinkedIn}
    \hspace{0.35cm}
    \href{https://benjaminschindler.vercel.app/}{Portfolio}
    \hspace{0.35cm}
    \href{https://github.com/BenjaSchindler}{GitHub}
\end{center}

\section*{Profile}
AI Engineer who builds and ships production LLM systems --- multi-agent workflows, RAG, recommendation flows, and the deterministic-agentic hybrid patterns that keep them safe in regulated domains. Owns systems end-to-end, from problem framing and evals to deployment and monitoring. Most recently CTO at Doctor911, where the AI products I designed and shipped contributed to a 10$\times$ increase in web traffic and the company reaching profitability.

\section*{Experience}
\begin{itemize}[left=0pt,noitemsep,nolistsep]

    \item \textbf{Doctor911} \hfill \textit{Mar. 2025 -- Present} \\
    \textit{Chief Technology Officer \& AI Engineering Lead (promoted)} \hfill \textit{Jan. 2026 -- Present} \\
    - Lead AI engineering and product across web, WhatsApp, and internal operations; own the AI roadmap and technical standards (evals, observability, HITL safety, CI/CD). \\
    - Shipped the AI products underpinning the company's 10$\times$ traffic increase and path to profitability; promoted IC $\rightarrow$ CTO in under a year. \\[2pt]
    \textit{AI Engineer} \hfill \textit{Mar. 2025 -- Jan. 2026} \\
    - Shipped two production multi-agent AI systems on LangGraph + GCP (Cloud Run, Vertex AI, CI/CD, monitoring; see \textit{Selected Projects}), plus an XGBoost medical exam recommender wired as a shared tool across agents. \\
    - Architected a deterministic-agentic hybrid pattern combining LangGraph orchestration with structured business rules for payments, booking, and doctor-in-the-loop clinical decisions. \\

    \item \textbf{WiseConn Latam} \hfill \textit{Sep. 2024 -- Mar. 2025} \\
    \textit{Data Science Intern} \\
    - Built CNN-based time-series forecasting for irrigation scheduling and classification models for solar installation analysis (see \textit{Selected Projects}). \\
    - Led a data governance initiative to organize company data across departments. \\
    - Integrated reproducible model workflows into AWS (SageMaker, S3) with validation and metric tracking. \\

    \item \textbf{Unitti} \hfill \textit{Jul. 2022 -- Jul. 2024} \\
    \textit{Jr. AI Engineer} \\
    - Developed Python APIs on PostgreSQL with automated testing, improving backend stability and query performance. \\
    - Built a Natural Language $\rightarrow$ SQL application (Flask, LLMs, Azure, GCP), improving SQL generation quality through user-feedback loops. \\

\end{itemize}

\section*{Selected Projects}
\begin{itemize}[left=0pt,noitemsep,nolistsep]
    \item \textbf{Doctor911 Conversational AI Platform} --- production multi-agent systems on LangGraph + FastAPI + Cloud Run spanning WhatsApp (4 agents: \textit{welcome}, \textit{commerce}, \textit{support}, \textit{async-order}) and Web (2 agents with a $\sim$100 ms semantic intent router). Form-based RAG recommender and an XGBoost exam recommender wired as shared tools; integrates Meta Flows, WhatsApp catalogs, Transbank, Supabase, and Cloud SQL.
    \item \textbf{Direct Client Work} --- two end-to-end AI products delivered for external clients. \textbf{MiAutoCheck:} multimodal, multi-agent used-vehicle valuation API (VLM inspection + 5 parallel research agents + supervisor consolidation $\rightarrow$ PDF reports; GPT-5-mini, Anthropic prompt caching, Tavily). \textbf{EPE:} workplace well-being platform with LLM safety guardrails (crisis / PII), per-user prompt A/B versioning, LLM-as-judge evals + drift monitoring, and Langfuse observability.
    \item \textbf{Doctor911 Internal Ops Agent (OpenClaw)} --- internal agent built on the OpenClaw open-source framework to automate team coordination, recurring operational tasks, and management workflows.
\end{itemize}

\section*{Education}
\begin{itemize}[left=0pt,itemsep=0.1em]
    \item \textbf{Universidad Adolfo Ibáñez} --- \textit{Master of Science in Data Science} \hfill \textit{GPA 4.0 / 4.0} \\
    Graduated with Maximum Distinction. Thesis (\textit{SMOTE-LLM}): hybrid LLM + embedding-space oversampling for imbalanced text classification; +2.25 pp over SMOTE.
    \item \textbf{Universidad Adolfo Ibáñez} --- \textit{Software Engineering} \& \textit{Industrial Engineering} \hfill \textit{GPA 3.7 / 4.0}
\end{itemize}

\section*{Technical Stack}
\begin{itemize}[left=0pt,noitemsep,nolistsep]
    \item \textbf{AI / ML:} LangGraph, LangChain, multi-agent orchestration, RAG (embeddings + vector retrieval), tool-calling, structured outputs, human-in-the-loop workflows, recommendation flows, Natural Language $\rightarrow$ SQL, forecasting. LLM providers: OpenAI, Anthropic, Gemini. Classical ML: XGBoost, PyTorch, TensorFlow, Pandas.
    \item \textbf{Serving, MLOps \& Cloud:} FastAPI, Docker, REST APIs, CI/CD, model \& LLM evals, observability and monitoring, structured logging; GCP (Cloud Run, Vertex AI, Cloud SQL), AWS (SageMaker, S3), Supabase, PostgreSQL, Linux.
    \item \textbf{Languages \& Frameworks:} Python, TypeScript, SQL/NoSQL, Next.js, React, Flask.
    \item \textbf{Spoken Languages:} Spanish (Native), English (Advanced), German (Basic).
\end{itemize}

\end{document}
